A Summery about reasoning with logic

### 2015-10-31 reasoning/summery.tex
removed the right weakening proof because I don't understand it and can't explain it. It doesn't confirm well to the structure I impose on induction.

\subparagraph{Definitions}
Natural numbers are all integers bigger than 0.
\[Even(n) = \left\{ \begin{matrix}
	n=0 &\\ 
	Even(n-2)& 
	\end{matrix}
\right \]

>>>>

\subparagraph{Definitions}
Natural numbers are all integers bigger than 0.

\[
Even(n) := \left\{
	\begin{array}{l}
		n= 0 \\
		Even(n-2)
	\end{array}
\right.
\]
\[
Odd(n) := \left\{
	\begin{array}{l}
		n= 1 \\
		Odd(n-2)
	\end{array}
\right.
\]

\subparagraph{Strategy}
All Natural numbers are either odd or even, this will be proven by induction.

\subparagraph{Proof} \emph{In here we look at the definitions and try to see
the base case(s)}. In case n=0, n is even according to the definition of
even, so n is either postivie or negative. \emph{reflecting back on what
we're trying to prove, saying its the case}

In case n=1, n is odd according to the definition of odd. So n is either
odd or even.

\emph{After the base case, first assume, then push with help of the definition}
Assume n is odd or even, then n+2 is also odd or even according to the
definition of odd or even.
